```{r echo = FALSE}
knitr::opts_chunk$set(
echo = FALSE,
message = FALSE,
warning = FALSE
)
```

## label
**1. Create one plot on the fuel economy data with customized title , subtitle ,
   caption , x , y , and colour labels.**

```{r fuel_plot}
mpg %>%
    ggplot(aes(displ, cty)) +
    geom_point(aes(color = class)) +
    geom_smooth(aes(color = class), se = FALSE) +
    geom_smooth(color = "black") +
    labs(title = "Look at that curve",
    subtitle = "With the standard error and everything!",
    caption = "Made by a data scientist",
    x = "Engine Displacement (l)",
    y = "City miles per gallon",
    color = "Vehicle class")
```

**2. The geom_smooth() is somewhat misleading because the hwy for large engines
   is skewed upwards due to the inclusion of light‐weight sports cars with big
   engines. Use your modeling tools to fit and display a better model.**

```{r fuel_mod}
mod <- lm(hwy ~ displ * class, data = mpg)
av_mod <- MASS::rlm(hwy ~ poly(displ,2), data = mpg)

mpg <- mpg %>% 
    gather_residuals(interaction = mod, rls = av_mod) %>%
    gather_predictions(interaction = mod, rls = av_mod)
```

```{r fuel_mod_plot}
mpg %>%
    ggplot(aes(displ, hwy)) +
    geom_point(aes(color = class)) +
    geom_line(data = filter(mpg, model == "interaction"),
              aes(y = pred, color = class)) +
    geom_line(data = filter(mpg, model == "rls"),
              aes(y = pred), size = 1.5, color = "black", alpha = 0.2) +
    labs(title = "Look at that curve",
    subtitle = "With the standard error and everything!",
    caption = "Made by a data scientist",
    x = "Engine Displacement (l)",
    y = "Highway miles per gallon",
    color = "Vehicle class")
```

**3. Take an exploratory graphic that you’ve created in the last month, and add
   informative titles to make it easier for others to understand.**

## annotations
**1. Use geom_text() with infinite positions to place text at the four corners of
   the plot.**

```{r fuel_mod_plot_annot}
mpg %>%
    ggplot(aes(displ, hwy)) +
    geom_point(aes(color = class)) +
    geom_line(data = filter(mpg, model == "interaction"),
              aes(y = pred, color = class)) +
    geom_line(data = filter(mpg, model == "rls"),
              aes(y = pred), size = 1.5, color = "black", alpha = 0.2) +
    labs(title = "Look at that curve",
    subtitle = "With the standard error and everything!",
    caption = "Made by a data scientist",
    x = "Engine Displacement (l)",
    y = "Highway miles per gallon",
    color = "Vehicle class") +
    geom_text(aes(Inf, Inf, label = "TEST"),
              hjust = "right", vjust = "top")
```

**2. Read the documentation for annotate() . How can you use it to add a text
   label to a plot without having to create a tibble? _ANS: just pass them in
   as stand along vector objects._**

**3. How do labels with geom_text() interact with faceting? How can you add a
   label to a single facet? How can you put a different label in each facet?
   (Hint: think about the underlying data.)**

```{r label}
label <- tibble(displ = Inf,
                hwy = Inf,
                class = unique(mpg$class),
                label = str_c("Put me on\n", class))
```

```{r fuel_mod_plot_annot_facet}
mpg %>%
    ggplot(aes(displ, hwy)) +
    geom_point(aes(color = class)) +
    geom_line(data = filter(mpg, model == "interaction"),
              aes(y = pred, color = class)) +
    geom_line(data = filter(mpg, model == "rls"),
              aes(y = pred), size = 1.5, color = "black", alpha = 0.2) +
    labs(title = "Look at that curve",
    subtitle = "With the standard error and everything!",
    caption = "Made by a data scientist",
    x = "Engine Displacement (l)",
    y = "Highway miles per gallon",
    color = "Vehicle class") +
    geom_text(aes(label = label), data = label,
              hjust = "right", vjust = "top") +
    facet_wrap(~ class)
```

**4. What arguments to geom_label() control the appearance of the background
   box? _ANS: label.padding, label.r, label.size, 'fill' aesthetics_**

**5. What are the four arguments to arrow() ? How do they work? Create a series
   of plots that demonstrate the most important options.**


```{r arrow_params}
arrow_params <- tibble(arrows = c(
                       ))
```

```{r plot_arrows}
ggplot() +
    geom_segment(aes(x = 0.1, y = 0, xend = 0.1, yend = 1),
                 arrow = arrow(angle = 0,
                               length = unit(0.2, "cm"),
                               ends = "last", type = "open")) +
    geom_segment(aes(x = 0.5, y = 0, xend = 0.5, yend = 1),
                 arrow = arrow(angle = 45,
                               length = unit(0.4, "cm"),
                               ends = "first", type = "closed")) +
    geom_segment(aes(x = 1, y = 0, xend = 1, yend = 1),
                 arrow = arrow(angle = 90,
                               length = unit(0.6, "cm"),
                               ends = "both", type = "open"))
```

## scales
**1. Why doesn’t the following code override the default scale? _ANS: the
'fill' variable wasn't provided_**

```{r}
ggplot(df, aes(x, y)) +
    geom_hex() +
    scale_color_gradient(low = "white", high = "red") +
    coord_fixed()
```

**2. What is the first argument to every scale? How does it compare to labs() ? 
   _ANS: `name` (same as the labs() functions.**

**3. Change the display of the presidential terms by:**

```{r}
presidential %>%
    mutate(id = 33 + row_number()) %>%
    ggplot(aes(start, id, color = party)) +
    geom_point() +
    geom_segment(aes(xend = end, yend = id)) +
    scale_colour_manual(
                        values = c(Republican = "pink", Democratic = "green")
    )
```

**a. Combining the two variants shown above.**

**b. Improving the display of the y-axis. _ANS: Done_**

**c. Labeling each term with the name of the president. _ANS: Done_**

**d. Adding informative plot labels._ANS: Done_**

**e. Placing breaks every four years (this is trickier than it seems!)._ANS:
   Done_**


```{r}
num_to_str_lab <- function(x) {
    suffix <- "th"
    last <- str_sub(x, -1, -1)
    if (last == "1") {
    suffix <- "st" 
    } else if (last == "2") {
    suffix <- "nd"
    } else if (last == "3") {
    suffix <- "rd"
    }
    return (map(x, ~paste0(., suffix)))
}
```

```{r}
term_starts <- seq(1952, 2020, by = 4)
presidential %>%
    mutate(id = 33 + row_number()) %>%
    ggplot(aes(start, id, color = party)) +
    geom_point() +
    geom_segment(aes(xend = end, yend = id)) +
    scale_colour_manual(values = c(Republican = "pink", Democratic = "green")) +
    scale_x_date(labels = str_c(term_starts), 
                 breaks = as_date(ISOdate(term_starts, 1, 1))) +
    scale_y_continuous(labels = map(seq(30, 50, by = 1), num_to_str_lab), 
                       breaks = seq(30, 50, by = 1)) +
    labs(x = "Starting year and term span", y = "Nth President") +
    geom_text(aes(label = name), nudge_y = 0.3)
```
as_date(ISOdate(seq(1960, 2020, by = 4), 1, 1))

**4. Use override.aes to make the legend on the following plot easier to see:**

```{r}
ggplot(diamonds, aes(carat, price)) +
    geom_point(aes(color = cut), alpha = 1/20) +
    guides(color = guide_legend(override.aes = list(alpha = 1)))

```
