```{r}
knitr::opts_chunk$set(
echo = FALSE
)
```

## code chunks

**1. Add a section that explores how diamond sizes vary by cut, colour, and
   clarity. Assume you’re writing a report for someone who doesn’t know R, and
   instead of setting echo = FALSE on each chunk, set a global option.**

```{r diamonds}
cut_numbers <- diamonds %>%
    filter(cut == "Fair") %>%
    group_by(cut) %>%
    count()
```
There are `r cut_numbers$n` Fair diamonds.

**2. Download diamond-sizes.Rmd from
   https://github.com/hadley/r4ds/tree/master/rmarkdown. Add a section that
   describes the largest 20 diamonds, including a table that displays their
   most important attributes.**

```{r largest 20 diamonds}
largest_20 <- diamonds %>%
    arrange(desc(z)) %>%
    head(20) %>%
    dplyr::select(-c(x, y))
```

```{r summar table}
largest_20 %>%
    summary() %>%
    head(6) %>%
    knitr::kable(caption = "summary statistics for 20 largest diamonds")
```

**3. Modify diamonds-sizes.Rmd to use comma() to produce nicely formatted
   output. Also include the percentage of diamonds that are larger than 2.5
   carats.**

```{r comma function}
comma <- function(x) {
    format(x, digits = 2, big.mark = ",")
}
```

There are ***not*** `r comma(cut_numbers$n*135)` Fair diamonds!

**4. Set up a network of chunks where d depends on c and b, and both b and c
   depend on a. Have each chunk print lubridate::now(), set cache = TRUE, then
   verify your understanding of caching.**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

```{r a}
lubridate::now()
```

```{r b, cached = TRUE, dependson = "a"}
lubridate::now()
```

```{r c, cached = TRUE, dependson = c("a", "b")}
lubridate::now()
```

```{r d, cached = TRUE, dependson = "c"}
lubridate::now()
```
